Abstract Data Type Inference

### 2015-03-07 algebra.tex
Added not-a-wqo example.

  $\preceq$ is not a wqo.

@@

>>>>

  Consider the infinite history sequence $h_1 h_2 \ldots$ where each $h_i$
  contains $2i$ operations $o_1, o_1', \ldots, o_i, o_i'$ where each $o_j$ is a
  completed {\tt push} operation matching itself, and each $o_j'$ is a pending
  {\tt pop} operation with undefined matching. Because each successive $h_i$
  has both more matches and more pending operations, no two histories of the
  sequence are related by $\preceq$. Thus $\preceq$ is not a wqo.

@@

The previous example demonstrates that $\preceq$ is not a wqo by allowing each
history $h_i$ of the infinite sequence to contain more and more pending
operations in order to ensure that $h_j \not\preceq h_i$ for every $j < i$.
Curbing this ability by limiting the maximum amount of pending operations per
history makes $\preceq$ a wqo. Although limiting to $k$ pending operations
essentially limits us to histories of executions with at most $k$ operations
parallel at any moment — e.g.,~of programs with at most $k$ threads — this
restriction comes at no loss of completeness when considering atomic ATD
kernels, whose histories are limited to $k\!=\!1$ pending operation.

TODO COMMENT ON CONCURRENCY-AWARE KERNELS
